---
title: "10_brow_analysis"
output: html_document
---

# load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
library(beepr)
```

# read in data 
```{r}
df <- read_csv(here::here("data", "adult_child_combined", "zdiff_binscreened2.csv"))
```




# fix data types

The emotion variable below is numbers so not sure how the emotion %in% c(happy, angry) was working. Add emo variable with emotion labels
```{r}
df$emotion <- as.factor(df$emotion)

levels(df$emotion)

df <- df %>% mutate_if(is.character, as.factor)

glimpse(df)
```



# BROW happy-angry child

### Make brow HA child df 

just happy/angry child face for cheek

```{r}
HA_child_brow <- df %>%
  filter(emo %in% c("happy", "angry")) %>%
  filter(muscle == "brow") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(HA_child_brow)

```



#Fix factor levels

```{r}

HA_child_brow$emo <- fct_relevel(HA_child_brow$emo, c("happy", "angry", "fear", "sad"))

levels(HA_child_brow$emo)



HA_child_brow$bin <- fct_relevel(HA_child_brow$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(HA_child_brow$bin)
```


## fit model 1 

This is the model structure we will use to check assumptions. Include all predicted fixed effects and simplest random effect structure (just intercepts for participant). In all likelihood this model with zscores as DV will not meet assumptions and we will need to transform data. 

```{r}
child_brow_lm <- lmer(zdiff ~ emo + bin + emo*bin + (1|pp_no), data = HA_child_brow, REML = FALSE)

```


### check assumptions
```{r}
plot(child_brow_lm)

qqnorm(resid(child_brow_lm))
qqline(resid(child_brow_lm))
```

As suscepted, need to transform to correct normality. 

### compute log_modulus


```{r}
HA_child_brow <- HA_child_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```

### fit model again

```{r}
child_brow_lm_new <- lmer(log_modulus ~ emo + bin + emo*bin + (1|pp_no), data = HA_child_brow, REML = FALSE)

```

### check assumptions again
```{r}
plot(child_brow_lm_new)

qqnorm(resid(child_brow_lm_new))
qqline(resid(child_brow_lm_new))
```
### compute new log mod

```{r}
HA_child_brow <- HA_child_brow %>%
  mutate(log_modulus_new = sign(zdiff) * log(1+abs(zdiff)))
```

### try fit model again

```{r}
child_brow_lm_1 <- lmer(log_modulus_new ~ emo + bin + emo*bin + (1|pp_no), data = HA_child_brow, REML = FALSE)

```

### check assumptions again
```{r}
plot(child_brow_lm_1)

qqnorm(resid(child_brow_lm_1))
qqline(resid(child_brow_lm_1))
```

#get anova, summary and tidy 

```{r}
anova(child_brow_lm_1)
```

```{r}
summary(child_brow_lm_1)
```

```{r}
tidy_child_brow1 <- tidy(child_brow_lm_1)
```

# fit model 2 (slopes for emotion)

```{r}
child_brow_lm_2 <- lmer(log_modulus_new ~ emo + bin + emo*bin + (1 + emo|pp_no), data = HA_child_brow, REML = FALSE)
```

#get anova, summary and tidy 

```{r}
anova(child_brow_lm_2)
```

```{r}
summary(child_brow_lm_2)
```

```{r}
tidy_child_brow2 <- tidy(child_brow_lm_2)
```

## check fit

```{r}
AIC(child_brow_lm_1)
AIC(child_brow_lm_2)
```

```{r}
anova(child_brow_lm_1, child_brow_lm_2)
```

#model take home - the model with the addition of a slope for emotion provides a better fit for the data than the model without 

# fit model 3 (slope for emotion and bin) - failed to converge

```{r}
child_brow_lm_3 <- lmer(log_modulus_new ~ emo + bin + emo*bin + (1 + emo + bin|pp_no), data = HA_child_brow, REML = FALSE)
```


```{r}
anova(child_brow_lm_2, child_brow_lm_3)
```

```{r}
AIC(child_brow_lm_2)
AIC(child_brow_lm_3)
```

# model 3 failed to converge, model 2 provides the best fit 


#get confidence intervals 
```{r}
confint.merMod(child_brow_lm_2, level = 0.95)
```

```{r}

really_nice_table <- dust(child_brow_lm_2) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table

```

#now do the same for adult 

### Make brow HA adult df 

just happy/angry child face for cheek

```{r}
HA_adult_brow <- df %>%
  filter(emo %in% c("happy", "angry")) %>%
  filter(muscle == "brow") %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(HA_adult_brow)

```


#Fix factor levels

```{r}

HA_adult_brow$emo <- fct_relevel(HA_adult_brow$emo, c("happy", "angry", "fear", "sad"))

levels(HA_adult_brow$emo)



HA_adult_brow$bin <- fct_relevel(HA_adult_brow$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(HA_adult_brow$bin)
```


## fit model 1 


```{r}
adult_brow_lm <- lmer(zdiff ~ emo + bin + emo*bin + (1|pp_no), data = HA_adult_brow, REML = FALSE)

```


### check assumptions
```{r}
plot(adult_brow_lm)

qqnorm(resid(adult_brow_lm))
qqline(resid(adult_brow_lm))
```

As suscepted, need to transform to correct normality. 

### compute log_modulus


```{r}
HA_adult_brow <- HA_adult_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```

### fit model again

```{r}
adult_brow_lm_new <- lmer(log_modulus ~ emo + bin + emo*bin + (1|pp_no), data = HA_adult_brow, REML = FALSE)

```

### check assumptions again
```{r}
plot(adult_brow_lm_new)

qqnorm(resid(adult_brow_lm_new))
qqline(resid(adult_brow_lm_new))
```
### compute new log mod

```{r}
HA_adult_brow <- HA_adult_brow %>%
  mutate(log_modulus_new = sign(zdiff) * log(1+abs(zdiff)))
```

### try fit model again

```{r}
adult_brow_lm_1 <- lmer(log_modulus_new ~ emo + bin + emo*bin + (1|pp_no), data = HA_adult_brow, REML = FALSE)

```

### check assumptions again
```{r}
plot(adult_brow_lm_1)

qqnorm(resid(adult_brow_lm_1))
qqline(resid(adult_brow_lm_1))
```


# get anova, summary and tidy

```{r}
anova(adult_brow_lm_1)
```

```{r}
summary(adult_brow_lm_1)
```
```{r}
tidy_adult_brow1 <- tidy(adult_brow_lm_1)
```

## fit model 2 (slope for emotion)

```{r}
adult_brow_lm_2 <- lmer(log_modulus_new ~ emo + bin + emo*bin + (1 + emo|pp_no), data = HA_adult_brow, REML = FALSE)
```

#get anova, summary, and tidy 

```{r}
anova(adult_brow_lm_2)
```

```{r}
summary(adult_brow_lm_2)
```

```{r}
tidy_adult_brow2 <- tidy(adult_brow_lm_2)
```


#check fit

```{r}
AIC(adult_brow_lm_1)
AIC(adult_brow_lm_2)
```

```{r}
anova(adult_brow_lm_1, adult_brow_lm_2)
```
#model take home - model with slope for emotion provides a better fit for the data than model without slope for emotion 

#fit model 3 (slope for emo and bin) - failed to converge
```{r}
adult_brow_lm_3 <- lmer(log_modulus_new ~ emo + bin + emo*bin + (1 + emo + bin|pp_no), data = HA_adult_brow, REML = FALSE)

```

#check fit 

```{r}
AIC(adult_brow_lm_2)
AIC(adult_brow_lm_3)
```
```{r}
anova(adult_brow_lm_2, adult_brow_lm_3)
```

#model take home - model 2 with just slope for emotion provides the best fit for the data


#get confidence intervals 
```{r}
confint.merMod(adult_brow_lm_2, level = 0.95)
```

```{r}

really_nice_table <- dust(adult_brow_lm_2) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```







































