---
title: "adult_child_test"
output: html_document
---


# load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
library(beepr)
library(ggplot2) 
library(ggeasy)
library(dplyr)
library(papaja)
```

Goal here is to work out whether it is possible to compare responses to child and adult faces i.e. to include model in the model. 

# read in data 
```{r}
df <- read_csv(here::here("data", "adult_child_combined", "zdiff_binscreened2.csv"))
```

# fix data types

add log modulus

```{r}

df <- df %>% mutate_if(is.character, as.factor) %>%
  mutate(log_modulus = sign(zdiff) * log(1+abs(zdiff)))
  

glimpse(df)
```

# CHEEK happy-angry 

### Make cheek df 

cheek

```{r}
cheek_data <- df %>%
  filter(emo %in% c("happy", "angry","fear", "sad")) %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, model, trial, bin)

cheek_data$emo <- fct_relevel(cheek_data$emo, c("happy", "angry", "fear", "sad"))

cheek_data$bin <- fct_relevel(cheek_data$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(cheek_data$bin)
```

add "model" to best fit from 9_cheek_analysis 

## model 1 (slopes emo)

This model adds model to best fit model (including slopes for emo)

> adult_cheek_lm_2 <- lmer(log_modulus ~ emo + bin + emo*bin + (1 + emo|pp_no) , data = HA_adult_cheek, REML = FALSE)

```{r}
cheek_lm_1 <- lmer(log_modulus ~ emo + bin + model + 
                    emo*bin + bin*model +
                    emo*bin*model +
                    (1 + emo|pp_no) , 
                  data = cheek_data, REML = FALSE)

beepr::beep()
```


## model 2 (just intercepts participant)
```{r}
cheek_lm_2 <- lmer(log_modulus ~ emo + bin + model + 
                    emo*bin + bin*model +
                    emo*bin*model +
                    (1|pp_no) , 
                  data = cheek_data, REML = FALSE)

beepr::beep()
```


# compare models with and without slopes

Model with slope does better than model without. 

```{r}
AIC(cheek_lm_1)
AIC(cheek_lm_2)

anova(cheek_lm_1, cheek_lm_2)
```

### get summary/tidydf

```{r}
summary(cheek_lm_1)

tidy_cheek1 <- tidy(cheek_lm_1)
```

#plot cheek data for all emo 

```{r}
cheek_plot <- cheek_data %>%
  arrange(pp_no, model, trial, bin)

```


#create new column called time_bin
```{r}

cheek_plot$time_bin <- cheek_plot$bin


cheek_plot <- cheek_plot %>%
  mutate(time_bin = recode(bin, "diff_bin1" = "100",
                                "diff_bin2" = "200", 
                                "diff_bin3" = "300", 
                                "diff_bin4" = "400", 
                              "diff_bin5" = "500", 
                              "diff_bin6" = "600", 
                              "diff_bin7" = "700", 
                              "diff_bin8" = "800",
                              "diff_bin9" = "900",
                              "diff_bin10" = "1000", .default = "NA"))
                           
```


```{r}
plot <- cheek_plot %>%
  group_by(time_bin, model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = model, colour = model)) +
  geom_point() +
  geom_line() +
  scale_colour_grey(start = 0.2, end = 0.6) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(colour = "black", size = 1)) +
  facet_wrap(~emo) +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in muscle activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 12) +
 easy_y_axis_title_size(size = 12)

print(plot)
```


#plot averaged across bins

```{r}
plot <- cheek_plot %>%
  group_by(model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = emo, y = meanZ, fill = model)) +
  geom_col(position = "dodge") +
  theme_apa(base_size = 14) +
  scale_fill_grey(start = 0.2, end = 0.9) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4, position = position_dodge(.9)) +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(colour =  "black", size = 1)) +
  scale_y_continuous(limits = c(-0.1, 0.1)) +
  labs(y = "Mean z-score difference (RMS) from baseline
(averaged across bins)", x = "Emotion") +
  easy_x_axis_title_size(size = 12) +
  easy_y_axis_title_size(size = 12)
  
print(plot)

```



# BROW - now do the same for brow 

###all emotions for brow 

```{r}
brow_data <- df %>%
  filter(emo %in% c("happy", "angry", "fear", "sad")) %>%
  filter(muscle == "brow") %>%
  arrange(pp_no, model, trial, bin)

brow_data$emo <- fct_relevel(brow_data$emo, c("happy", "angry", "fear", "sad"))

brow_data$bin <- fct_relevel(brow_data$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(brow_data$bin)
```

add "model" to best fit from 10_brow_analysis 

## model 1 (slopes emo)

This model adds model to best fit model (including slopes for emo)

> child_brow_lm_2 <- lmer(log_modulus_new ~ emo + bin + emo*bin + (1 + emo|pp_no), data = HA_child_brow, REML = FALSE)

```{r}
brow_lm_1 <- lmer(log_modulus ~ emo + bin + model + 
                    emo*bin + bin*model +
                    emo*bin*model +
                    (1 + emo|pp_no) , 
                  data = brow_data, REML = FALSE)

beepr::beep()
```

does it do better than model without slopes for emo? 

## model 2 (just intercepts participant)
```{r}
brow_lm_2 <- lmer(log_modulus ~ emo + bin + model + 
                    emo*bin + bin*model +
                    emo*bin*model +
                    (1|pp_no) , 
                  data = brow_data, REML = FALSE)

beepr::beep()
```

# compare models with and without slopes

yes model with slope does better than model without. 

```{r}
AIC(brow_lm_1)
AIC(brow_lm_2)

anova(brow_lm_1, brow_lm_2)
```



### get summary/tidydf
```{r}
summary(brow_lm_1)

tidy_brow1 <- tidy(brow_lm_1)
```


# plot brow 

#plot cheek data for all emo 

```{r}
brow_plot <- brow_data %>%
  arrange(pp_no, model, trial, bin)

```


#create new column called time_bin
```{r}

brow_plot$time_bin <- brow_plot$bin


brow_plot <- brow_plot %>%
  mutate(time_bin = recode(bin, "diff_bin1" = "100",
                                "diff_bin2" = "200", 
                                "diff_bin3" = "300", 
                                "diff_bin4" = "400", 
                              "diff_bin5" = "500", 
                              "diff_bin6" = "600", 
                              "diff_bin7" = "700", 
                              "diff_bin8" = "800",
                              "diff_bin9" = "900",
                              "diff_bin10" = "1000", .default = "NA"))
                           
```



```{r}
plot <- brow_plot %>%
  group_by(time_bin, model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = model, colour = model)) +
  geom_point() +
  geom_line() +
  scale_colour_grey(start = 0.2, end = 0.6) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(colour = "black", size = 1)) +
  facet_wrap(~emo) +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in muscle activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 12) +
 easy_y_axis_title_size(size = 12)

print(plot)
```



#plot averaged across bins

```{r}
plot <- brow_plot %>%
  group_by(model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = emo, y = meanZ, fill = model)) +
  geom_col(position = "dodge") +
  theme_apa(base_size = 14) +
  scale_fill_grey(start = 0.2, end = 0.9) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4, position = position_dodge(.9)) +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(colour =  "black", size = 1)) +
  scale_y_continuous(limits = c(-0.1, 0.1)) +
  labs(y = "Mean z-score difference (RMS) from baseline
(averaged across bins)", x = "Emotion") +
  easy_x_axis_title_size(size = 12) +
  easy_y_axis_title_size(size = 12)
  
print(plot)

```

















